Understanding the Data Duplication in VM Cloud Storage

### 2012-03-18 data_analysis/overall.tex
uodate

\section{Overall Deduplication Effect}
Our study start from examining the effect of complete deduplication over both data sets.
Each virtual disk image is divided into small variable-sized blocks using the TTTD algorithm\cite{frame05},
under the average 4KB, maximum 16KB and minimum 4KB setting. Complete deduplication is
done by caculating the SHA-1 hash of each block and identifying duplicate copies base on compare-by-hash.

>>>>

\section{Overall Deduplication Effect}
Our study start from examining the effect of complete deduplication over both data sets.
Each virtual disk image is divided into small variable-sized blocks using the TTTD algorithm\cite{frame05},
under the average 4KB, maximum 16KB and minimum 2KB setting. Complete deduplication is
done by caculating the SHA-1 hash of each block and identifying duplicate copies base on compare-by-hash.
